Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-10 analysis/study2.qmd
typos

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10 <- cbind(data$df10, scores$sample10)
df11 <- cbind(data$df11, scores$sample11)
df12 <- cbind(data$df12, scores$sample12)
df13 <- cbind(data$df13, scores$sample12)
df14 <- cbind(data$df14, scores$sample14)
df15 <- cbind(data$df15, scores$sample15)

@@

pool_coef <- function(with = "Age", component = "Demographic", standardize="within") {
  rez <- data.frame()
  for(intero in vars_intero) {
    data <- data.frame() 
    for(dataset in list(df1a, df1b, df2, df3, df4, 
                     df5, df6, df7a, df7b, df7c, 
                     df8a, df8b, df9, df10, df11, 
                     df12, df14, df15)) {
      if (with %in% names(dataset)) {
        d <- dataset[c(with, intero, "Sample")]
        if(standardize == "within") d <- standardize(d)
        data <- rbind(data, d)
      }
    }

    if(standardize == "between") {
      data <- standardize(data[complete.cases(data), ])
    }

    if (with == "Gender") {
      data <- data[data$Gender != "Other",]
      data$Gender <- factor(data$Gender, levels = c("Male", "Female"))
      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
    } else {
      f <- as.formula(paste0(with, "~", intero, " + (", intero, "|Sample)"))
      f2 <- as.formula(paste0(with, "~", intero, " + (1|Sample)"))
    }

    # if(length(unique(data$Sample)) == 1)
    m <- glmmTMB::glmmTMB(f, data = data)
    type <- "Full"
    if(!insight::is_converged(m)) {
      m <- glmmTMB::glmmTMB(f2, data = data)
      type <- "Reduced"
    }
    out <- parameters::parameters(m)[2, ] |> 
      select(r = Coefficient, CI_low, CI_high, p) |> 
      as.data.frame()
    out$var_Interoception <- intero
    out$var_Correlate <- with
    out$Component <- component
    out$Method <- standardize
    out$Type <- type
    out$Converged <- insight::is_converged(m)
    rez <- rbind(rez, out)

  }
  rez
}

make_rez <- function(with = "Gender", component = "Demographic", name = with) {
  d <- rbind(
    pool_coef(with = with, component = component, standardize="within"),
    pool_coef(with = with, component = component, standardize="between")) 
  d$var_Correlate <- name
  d
}

data <- make_rez(with = "Gender", component = "Demographic", name = "Gender (Female - Male)")
```

@@

data <- rbind(data, make_rez(with = "Age", component = "Demographic"))
```

@@

data <- rbind(
  data,
  make_rez(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation"),
  make_rez(with = "MAIA_BodyListening", component = "MAIA", name = "Listening"),
  make_rez(with = "MAIA_BodyTrusting", component = "MAIA", name = "Trusting"),
  make_rez(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness"),
  make_rez(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting"),
  make_rez(with = "MAIA_Noticing", component = "MAIA", name = "Noticing"),
  make_rez(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying"),
  make_rez(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation"),
  make_rez(with = "MAIA_Trusting", component = "MAIA", name = "Trusting")
)

```

@@

p <- data |>
  filter(Method == "within") |> 
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate")) |>
         # Component = fct_relevel(
         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
  ggplot(aes(x = var_Correlate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
  geom_linerange(aes(color = dir, alpha = sig, ymin = CI_low, ymax = CI_high), linewidth = 2) +
  # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
  #                linewidth = 1) +
  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
  scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  coord_flip(ylim = c(-0.5, 0.5)) +
  theme_modern(axis.title.space = 5) +
  labs(y = "Strength of Association (std. Beta)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure3.png", p, width=21*0.5, height=29.7*0.5, dpi=300, bg="white")
```

>>>>

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10 <- cbind(data$df10, scores$sample10)
df11 <- cbind(data$df11, scores$sample11)
df12 <- cbind(data$df12, scores$sample12)
df13 <- cbind(data$df13, scores$sample13)
df14 <- cbind(data$df14, scores$sample14)
df15 <- cbind(data$df15, scores$sample15)

@@

pool_coef <- function(with = "Age", component = "Demographic", name = with, unequalrange=FALSE) {
  rez <- data.frame()
  for(intero in vars_intero) {
    data <- data.frame() 
    for(dataset in list(df1a, df1b, df2, df3, df4, 
                     df5, df6, df7a, df7b, df7c, 
                     df8a, df8b, df9, df10, df11, 
                     df12, df14, df15)) {
      if (with %in% names(dataset)) {
        d <- dataset[c(with, intero, "Sample")]
        data <- rbind(data, d)
      }
    }

    # Make sure that min-max of "with" is the equal across all samples
    check <- summarize(data, 
                       min = min(!!sym(with), na.rm = TRUE),  
                       max = max(!!sym(with), na.rm = TRUE), .by = "Sample")
    if (with != "Gender" && (any(check$min != min(check$min)) || any(check$max != max(check$max)))) {
      if(unequalrange == FALSE) {
        print(check)
        stop(paste0("The range of '", with, "' is not equal across samples."))
      }
    }

    data <- standardize(data[complete.cases(data), ])

    if (with == "Gender") {
      data <- data[data$Gender != "Other",]
      data$Gender <- factor(data$Gender, levels = c("Male", "Female"))
      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
    } else {
      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
    }

    # if(length(unique(data$Sample)) == 1)
    m <- glmmTMB::glmmTMB(f, data = data)
    type <- "Full"
    if(!insight::is_converged(m)) {
      m <- glmmTMB::glmmTMB(f2, data = data)
      type <- "Reduced"
    }
    out <- parameters::parameters(m)[2, ] |> 
      select(r = Coefficient, CI_low, CI_high, p) |> 
      as.data.frame()
    out$var_Interoception <- intero
    out$var_Correlate <- with
    out$Component <- component
    out$Type <- type
    out$Converged <- insight::is_converged(m)
    out$N <- nrow(data)
    rez <- rbind(rez, out)

  }
  rez$var_Correlate <- name
  rez
}

data <- pool_coef(with = "Gender", component = "Demographic", name = "Gender (Female - Male)")
```

@@

data <- rbind(data, pool_coef(with = "Age", component = "Demographic", unequalrange=TRUE))
```

@@

data <- rbind(
  data,
  pool_coef(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation", unequalrange=TRUE),
  pool_coef(with = "MAIA_BodyListening", component = "MAIA", name = "Listening", unequalrange=TRUE),
  pool_coef(with = "MAIA_Trusting", component = "MAIA", name = "Trusting", unequalrange=TRUE),
  pool_coef(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness", unequalrange=TRUE),
  pool_coef(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting", unequalrange=TRUE),
  pool_coef(with = "MAIA_Noticing", component = "MAIA", name = "Noticing", unequalrange=TRUE),
  pool_coef(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying", unequalrange=TRUE),
  pool_coef(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation", unequalrange=TRUE)
)
```

@@

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate")) |>
         # Component = fct_relevel(
         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
  ggplot(aes(x = var_Correlate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
  geom_linerange(aes(color=dir, alpha=sig, ymax=r, ymin=0), linewidth = 1) +
  geom_linerange(aes(color = dir, alpha = sig, ymin = CI_low, ymax = CI_high, linewidth = log(N))) +
  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
  #                linewidth = 1) +
  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
  scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  scale_linewidth_continuous(range = c(3, 7), guide = "none") +
  coord_flip(ylim = c(-0.35, 0.35)) +
  theme_modern(axis.title.space = 5) +
  labs(y = "Strength of Association (std. Beta)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure3.png", p, width=21*0.5, height=29.7*0.5, dpi=300, bg="white")
```
